---
title: "Homework_10"
author: "Gillian Berglund"
date: "3/30/2022"
output: 
  html_document: 
    theme: cosmo
---
### Problem 1:
**Using a for loop, write a function to calculate the number of zeroes in a numeric vector**

```{r}
myvector <- rbinom(n=45,size = 1,prob = 0.9)
counter <- 0

for(i in 1:length(myvector)){
  if(myvector[i]==0)
    counter <- counter + 1
}

print(counter)
```

### Problem 2: 
**Use subsetting instead of a loop to rewrite the function as a single line of code.**

```{r}
myvectorsub <- myvector[myvector == 0]
length(myvectorsub)
```

### Problem 3:
**Write a function that takes as input two integers representing the number of rows and columns in a matrix.**

```{r}


#make_matrix <- function(row=5,col=6) {
  #mat <- matrix(nrow = row, ncol = col)
  
 # for(i in 1:row{
 # for(j in 1:col){
 #   mat[i,j] <- i*j
 # }
#  }
#}
    
```

### Problem 4: Practice calling custom functions within a for loop
**PART A: a dataset with 3 groups of data, each group drawn from a distribution with a different mean. The final data frame should have 1 column for group and 1 column for the response variable.**

```{r}
Group1 <- rnorm(10, mean = 5)
Group2 <- rnorm(10, mean = 2)
Group3 <- rnorm(10, mean = 8)

Groups <- c(rep("Group1",10),rep("Group2",10),rep("Group3",10))
ResVar <- c(Group1, Group2, Group3)
Group.df <- data.frame(Groups, ResVar) 
head(Group.df)

```

**PART B: Write a custom function that 1) reshuffles the response variable, and 2) calculates the mean of each group in the reshuffled data. Store the means in a vector of length 3.**

```{r}
library(dplyr)

shuffle_data <- function(){
  
  ShuffResVar <- sample(Group.df$ResVar)
  Shuff.df <- data.frame(Groups, ShuffResVar)
  
  Averages <- Shuff.df %>%
    group_by(Groups) %>%
    summarise_at(vars(ShuffResVar), list(name=mean))

  averages<-(Averages$name)
  
}


```

**PART C:Use a for loop to repeat the function in b 100 times. Store the results in a data frame that has 1 column indicating the replicate number and 1 column for each new group mean, for a total of 4 columns.**

```{r}



```

**PART D: Use qplot() to create a histogram of the means for each reshuffled group. Or, if you want a challenge, use ggplot() to overlay all 3 histograms in the same figure. How do the distributions of reshuffled means compare to the original means?**
```{r}



```



