---
title: "Homework_04"
author: "Gillian Berglund"
date: "2/9/2022"
output: 
  html_document: 
    theme: cosmo
---

### Problem 1 


``` {r}
x <- 1.1
a <- 2.2
b <- 3.3

z <- x^a^b
print(z)

z <- (x^a)^b
print(z)

z <- 3*x^3 + 2*x^2 + 1
print(z)
```

### Problem 2 

```{r}
a <- c(seq(from = 1, to = 8),seq(from = 7, to = 1))

b <- rep(1:5, c(1,2,3,4,5))

c <- rep(5:1, c(1,2,3,4,5))
  
```

### Problem 3
Create a vector of two random uniform number. In a spatial map, these can be interpreted as x and y coordinates that give the location of an individual (such as a marked forest tree in a plot that has been mapped). Using one of R’s inverse trigonometry functions (asin(), acos(), or atan()), convert these numbers into polar coordinates

```{r}
xy <- runif(2)
theta = atan(xy[2]/xy[1])
r = (xy[2]^2 + xy[1]^2)^0.5

```

### Problem 4

```{r}
#start: animals lined up to enter Noah’s Ark
queue <- c("sheep", "fox", "owl", "ant")

#a: the serpent arrives and gets in line 
queue <- c(queue,"serpent")

#b: the sheep enters the ark 
queue <- queue[! queue %in% c('sheep')]

#c: the donkey arrives and talks his way to the front of the line;
queue <- append(queue, "donkey", after = 0)

#d: the serpent gets impatient and leaves;
queue <- queue[! queue %in% c('serpent')]

#e: the owl gets bored and leaves;
queue <- queue[! queue %in% c('owl')]

#f: the aphid arrives and the ant invites him to cut in line.
queue <- append(queue, "aphid", after = 2)

#g:Finally, determine the position of the aphid in the line.
which(queue == "aphid")

```

### Problem 5
Use R to create a vector of all of the integers from 1 to 100 that are not divisible by 2, 3, or 7. 

```{r}

odd <- c(seq(from = 1, to = 100))
odd <- which(!odd %% 2 == 0, arr.ind = TRUE)
odd <- which(!odd %% 3 == 0, arr.ind = TRUE)
odd <- which(!odd %% 7 == 0, arr.ind = TRUE)


```
