---
title: "Homework_10"
author: "Gillian Berglund"
date: "3/30/2022"
output: 
  html_document: 
    theme: cosmo
---
### Problem 1:
**Using a for loop, write a function to calculate the number of zeroes in a numeric vector**

```{r}
myvector <- rbinom(n=45,size = 1,prob = 0.9)
counter <- 0

for(i in 1:length(myvector)){
  if(myvector[i]==0)
    counter <- counter + 1
}

print(counter)
```

### Problem 2: 
**Use subsetting instead of a loop to rewrite the function as a single line of code.**

```{r}
myvectorsub <- myvector[myvector == 0]
length(myvectorsub)
```

### Problem 3:
**Write a function that takes as input two integers representing the number of rows and columns in a matrix.**

```{r}

makemat <- function(x,y) {
  mat <- matrix(nrow = x, ncol = y)
  
  for(i in 1:nrow(mat)){
    for(j in 1:ncol(mat)){
     mat[i,j] <- i*j
    }
  }
  print(mat)
}

makemat(x=sample(1:10, 1),y=sample(1:10, 1))
```

### Problem 4: Practice calling custom functions within a for loop
**PART A: a dataset with 3 groups of data, each group drawn from a distribution with a different mean. The final data frame should have 1 column for group and 1 column for the response variable.**

```{r}
Group1 <- rnorm(10, mean = 5)
Group2 <- rnorm(10, mean = 2)
Group3 <- rnorm(10, mean = 8)

Groups <- c(rep("Group1",10),rep("Group2",10),rep("Group3",10))
ResVar <- c(Group1, Group2, Group3)
Group.df <- data.frame(Groups, ResVar) 
head(Group.df)

```

**PART B: Write a custom function that 1) reshuffles the response variable, and 2) calculates the mean of each group in the reshuffled data. Store the means in a vector of length 3.**

```{r}
library(dplyr)

shuffle_data <- function(){
  
  ShuffResVar <- sample(Group.df$ResVar)
  Shuff.df <- data.frame(Groups, ShuffResVar)
  
  Averages <- Shuff.df %>%
    group_by(Groups) %>%
    summarise_at(vars(ShuffResVar), list(name=mean))

  averages<-(Averages$name)
  
  return(averages)

}

shuffle_data()


```

**PART C:Use a for loop to repeat the function in b 100 times. Store the results in a data frame that has 1 column indicating the replicate number and 1 column for each new group mean, for a total of 4 columns.**

```{r}
# want to create an empty data frame. 
# use i to append onto data frame at [i] row 

n_sim <- 100

Replicate <- rep(NA, 100)
Group1 <- rep(NA, 100)
Group2 <- rep(NA, 100)
Group3 <- rep(NA, 100)

Randomization <- data.frame(Replicate,Group1,Group2,Group3)

for(i in seq_len(n_sim)){
   temp1 <- shuffle_data()
   
   Randomization[i,] <- c(i,temp1)
  
}

head(Randomization)

```

**PART D: Use qplot() to create a histogram of the means for each reshuffled group.How do the distributions of reshuffled means compare to the original means?**

```{r}
library(ggplot2)

g1 <- ggplot(data=Randomization,
             mapping=aes(x=Group1,fill=I("tomato"),color=I("black"))) + geom_histogram()
print(g1)

g2 <- ggplot(data=Randomization,
             mapping=aes(x=Group2,fill=I("tomato"),color=I("black"))) + geom_histogram()
print(g2)

g3 <- ggplot(data=Randomization,
             mapping=aes(x=Group3,fill=I("tomato"),color=I("black"))) + geom_histogram()
print(g3)

```

### Problem 5: Statistical Analysis 
**Standard Statistical Analysis of Group Means:**
```{r}
ano_model <- aov(ResVar~Groups,data=Group.df)
  z <- summary(ano_model)
  flat_out <- unlist(z)
  ano_stats <- list(f_ratio <- unlist(z)[7],
                    f_pval <- unlist(z)[9])

  print(ano_stats)

```
**p-values from randomization test** 

```{r}
library(tidyverse)

Rand_Anova <- pivot_longer(Randomization,Group1:Group3,names_to = "Groups", values_to = "ResVar")
head(Rand_Anova)
  
  
Rand_ano_model <- aov(ResVar~Groups,data=Rand_Anova)
  z2 <- summary(ano_model)
  flat_out2 <- unlist(z)
  Rand_ano_stats <- list(f_ratio <- unlist(z)[7],
                    f_pval <- unlist(z)[9])

  print(Rand_ano_stats)

```