---
title: "Homework_08"
author: "Gillian Berglund"
date: "3/16/2022"
output: 
  html_document: 
    theme: cosmo
---
# Creating Fake Data Sets To Explore Hypotheses


#### Expected pattern for a given hypothesis: 
If a given signaling molecule (G) is upregulating the transcription of another peptide in cells, you would expect greater abundance of peptides in cells treated with G

#### Creating Data that supports hypothesis 
```{r}
groupWith <- rnorm(n=45, mean = 0.84 , sd = 0.1)
hist(groupWith)

groupWithOut <- rnorm(n=45, mean = 0.33, sd = 0.12)
hist(groupWithOut)

DataFrame <- data.frame(1:45, groupWith, groupWithOut)
```

#### Creating a Random Data Frame (for ANOVA)

Followed ANOVA example used in class during Lecture 12

```{r}
n_group <- 2
n_name <- c("withG", "withoutG")
n_size <- c(45,45)
n_mean <- c(0.84,0.33)
n_sd <- c(0.1,0.12)

ID <- 1:sum(n_size)

proportions <- c(rnorm(n=n_size[1],mean=n_mean[1],sd=n_sd[1]),
             rnorm(n=n_size[2],mean=n_mean[2],sd=n_sd[2]))

trt_group <- rep(n_name,n_size)

ano_data <- data.frame(ID,trt_group,proportions)
head(ano_data)

```

#### Statistical Analysis & GG Plot

```{r}
ano_model <- aov(proportions~trt_group,data=ano_data)
print(ano_model)
z <- summary(ano_model)
print(z)
flat_out <- unlist(z)
ano_stats <- list(f_ratio <- unlist(z)[7],
                  f_pval <- unlist(z)[9])
print(ano_stats)

library(ggplot2)
ano_plot <- ggplot(ano_data) +
            aes(x=trt_group,y=proportions) +
            geom_boxplot()
print(ano_plot)
```

#### Adjusting Mean and effect sizes for Data Set
