---
title: "Homework_08"
author: "Gillian Berglund"
date: "3/16/2022"
output: 
  html_document: 
    theme: cosmo
---
# Creating Fake Data Sets To Explore Hypotheses


### 1. Expected pattern for a given hypothesis: 

If a given signaling molecule is upregulating the transcription of another protein in cells, you would expect a greater amount of mRNA for the protein in cells treated with the signaling molecule. 

Data set represents relative mRNA levels detected by rtPCR for protein X in cell populations. 

### 2 & 3. Creating Dataframe with Data that supports hypothesis 
```{r}
groupWith <- rnorm(n=15, mean = 0.72 , sd = 0.1)
groupWithOut <- rnorm(n=15, mean = 0.40, sd = 0.12)

hist(groupWith)
hist(groupWithOut)

DataFrame <- data.frame(1:15, groupWith, groupWithOut)
```

### 4. Creating a Random Data Frame (for ANOVA)

Followed ANOVA example used in class during Lecture 12

```{r}
n_group <- 2
n_name <- c("with", "without")
n_size <- c(15,15)
n_mean <- c(0.72,0.40)
n_sd <- c(0.1,0.12)

ID <- 1:sum(n_size)

proportions <- c(rnorm(n=n_size[1],mean=n_mean[1],sd=n_sd[1]),
             rnorm(n=n_size[2],mean=n_mean[2],sd=n_sd[2]))

trt_group <- rep(n_name,n_size)

ano_data <- data.frame(ID,trt_group,proportions)
head(ano_data)

```
#### Statistical Analysis & GG Plot

```{r}
ano_model <- aov(proportions~trt_group,data=ano_data)
print(ano_model)
z <- summary(ano_model)
print(z)
flat_out <- unlist(z)
ano_stats <- list(f_ratio <- unlist(z)[7],
                  f_pval <- unlist(z)[9])
print(ano_stats)

library(ggplot2)
ano_plot <- ggplot(ano_data) +
            aes(x=trt_group,y=proportions) +
            geom_boxplot()
print(ano_plot)
```

### 6. Adjusting Mean and Effect sizes for Data Set
With a sample size of 15, any effect size smaller than .12 won't reliably produce a significant result. 

### 7. Adjusting Sample Sizes:
With an effect size of .32 between groups, you would need a sample size of at least 5 to consistently get a significant result.  