---
title: "Homework_05"
author: "Gillian Berglund"
date: "2/16/2022"
output: 
  html_document: 
    theme: cosmo
---
### Problem 1
**Assign to the variable n_dims a single random integer between 3 and 10.**
```{r}
n_dims <- sample(3:10, 1)
print(n_dims)
```

**Create a vector of consecutive integers from 1 to n_dims2.**
```{r}
vector_consec <- seq(from=1, to =(n_dims)^2)
print(vector_consec)
```
**Use the sample function to randomly reshuffle these values.**
```{r}
sample(x=vector_consec)
```
**create a square matrix with these elements & print out the matrix.**
```{r}
m <- matrix(data=vector_consec,nrow=n_dims)
print(m)
```
**find a function in r to transpose the matrix.**
```{r}
tm <- t(m)
```
**print it out again and note how it has changed.**
```{r}
print(tm)
```
**calculate the sum and the mean of the elements in the first row and the last row.**
```{r}
first_row <- tm[1,]
last_row <- tm[n_dims,]

sum(first_row)
sum(last_row)

mean(first_row)
mean(last_row)
```
**read about the eigen() function and use it on your matrix**
```{r}
eigenm <- eigen(tm, only.values = FALSE, EISPACK = FALSE)
print(eigenm)
```
**look carefully at the elements of $values and $vectors. What kind of numbers are these? Dig in with the typeof() function to figure out their type.**
```{r}
typeof(eigenm$values)
typeof(eigenm$vectors)
```

### Problem 2
**Create a list with the following named elements:**   
**my_matrix, which is a 4 x 4 matrix filled with random uniform values**   
```{r}
my_data <- runif(16)
my_matrix <- matrix(data=my_data,nrow=4)
print(my_matrix)
```
**my_logical which is a 100-element vector of TRUE or FALSE values. Do this efficiently by setting up a vector of random values and then applying an inequality to it.**   
```{r}
logical <- sample(0:100, 100, replace=TRUE)
print(logical)
my_logical <- logical<50
print(my_logical)
```
**my_letters, which is a 26-element vector of all the lower-case letters in random order.**   
```{r}
my_letters <- sample(letters, size=26)
print(my_letters)
```
**create a new list, which has the element[2,2] from the matrix, the second element of the logical vector, and the second element of the letters vector.**
```{r}
my_list <- list(my_matrix[2,2],my_logical[2],my_letters[2])
print(my_list)
```
**use the typeof() function to confirm the underlying data types of each component in this list**
```{r}
typeof(my_list[[1]])
typeof(my_list[[2]])
typeof(my_list[[3]])
```
**combine the underlying elements from the new list into a single atomic vector with the c() function. What is the data type of this vector?** 
```{r}
condensed_list <- c(my_list[[1]],my_list[[2]],my_list[[3]])
print(condensed_list)
typeof(condensed_list)
```

### Problem 3
**Create a data frame with two variables (= columns) and 26 cases (= rows).**   

**call the first variable my_unis and fill it with 26 random uniform values from 0 to 10**
```{r}
my_unis <- runif(n=26,min=1,max=10)
print(my_unis)
```
**call the second variable my_letters and fill it with 26 capital letters in random order.**
```{r}
my_letters <- sample(LETTERS, size=26)
print(my_letters)
```
```{r}
dataFrame <- data.frame(my_unis,my_letters)
print(dataFrame)
```
**for the first variable, use a single line of code in R to select 4 random rows and replace the numerical values in those rows with NA.**
```{r}
dataFrame[sample(26, size = 4),1] <- NA
print(dataFrame)
```
**for the first variable, write a single line of R code to identify which rows have the missing values.**
```{r}
dataFrame[!complete.cases(dataFrame),]
```
**for the second variable, sort it in alphabetical order**
```{r}

```
**calculate the column mean for the first variable.**
```{r}

```