---
title: "Homework_06"
author: "Gillian Berglund"
date: "2/23/2022"
output: 
  html_document: 
    theme: cosmo
---
### Running Sample Code

```{r}
library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation
```

```{r}
# quick and dirty, a truncated normal distribution to work on the solution set

z <- rnorm(n=3000,mean=0.2)
z <- data.frame(1:3000,z)
names(z) <- list("ID","myVar")
z <- z[z$myVar>0,]
str(z)
summary(z$myVar)
```

**Plot histogram of data**
```{r}
p1 <- ggplot(data=z, aes(x=myVar, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(p1)
```
**Add empirical density curve**
```{r}
p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
print(p1)
```
**Get maximum likelihood parameters for normal**
```{r}
normPars <- fitdistr(z$myVar,"normal")
print(normPars) # provides mean and sd
str(normPars) # is a list of 5
normPars$estimate["mean"] # note structure of getting a named attribute
```
**Plot normal probability density**
```{r}
meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(z$myVar),len=length(z$myVar))

 stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(z$myVar), args = list(mean = meanML, sd = sdML))
 p1 + stat
```
**Plot exponential probability density**
```{r}
expoPars <- fitdistr(z$myVar,"exponential")
rateML <- expoPars$estimate["rate"]

stat2 <- stat_function(aes(x = xval, y = ..y..), fun = dexp, colour="blue", n = length(z$myVar), args = list(rate=rateML))
 p1 + stat + stat2
```
**Plot uniform probability density**
```{r}
stat3 <- stat_function(aes(x = xval, y = ..y..), fun = dunif, colour="darkgreen", n = length(z$myVar), args = list(min=min(z$myVar), max=max(z$myVar)))
 p1 + stat + stat2 + stat3
```
**Plot gamma probability density**
```{r}
gammaPars <- fitdistr(z$myVar,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="brown", n = length(z$myVar), args = list(shape=shapeML, rate=rateML))
 p1 + stat + stat2 + stat3 + stat4
```
**Plot beta probability density**
```{r}
pSpecial <- ggplot(data=z, aes(x=myVar/(max(myVar + 0.1)), y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
  xlim(c(0,1)) +
  geom_density(size=0.75,linetype="dotted")

betaPars <- fitdistr(x=z$myVar/max(z$myVar + 0.1),start=list(shape1=1,shape2=2),"beta")
shape1ML <- betaPars$estimate["shape1"]
shape2ML <- betaPars$estimate["shape2"]

statSpecial <- stat_function(aes(x = xval, y = ..y..), fun = dbeta, colour="orchid", n = length(z$myVar), args = list(shape1=shape1ML,shape2=shape2ML))
pSpecial + statSpecial
```

### Trying it with inputting data

```{r}
library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation
```

```{r}
# load in data
z <- read.table("raw_data.csv",header=TRUE,sep=",")
z <- data.frame(1:46,z$WhitePopVax)
head(z)
str(z)
summary(z)
```

**Plot histogram of data**
```{r}
p1 <- ggplot(data=z, aes(x=z.WhitePopVax, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(p1)
```
**Add empirical density curve**
```{r}
p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
print(p1)
```
**Get maximum likelihood parameters for normal**
```{r}
normPars <- fitdistr(z$z.WhitePopVax,"normal")
print(normPars) # provides mean and sd
str(normPars) # is a list of 5
normPars$estimate["mean"] # note structure of getting a named attribute
```
**Plot normal probability density**
```{r}
meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(z$z.WhitePopVax),len=length(z$z.WhitePopVax))

stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(z$z.WhitePopVax), args = list(mean = meanML, sd = sdML))
 p1 + stat
```
**Plot exponential probability density**
```{r}
expoPars <- fitdistr(z$z.WhitePopVax,"exponential")
rateML <- expoPars$estimate["rate"]

stat2 <- stat_function(aes(x = xval, y = ..y..), fun = dexp, colour="blue", n = length(z$z.WhitePopVax), args = list(rate=rateML))
 p1 + stat + stat2
```
**Plot uniform probability density**
```{r}
stat3 <- stat_function(aes(x = xval, y = ..y..), fun = dunif, colour="darkgreen", n = length(z$z.WhitePopVax), args = list(min=min(z$z.WhitePopVax), max=max(z$z.WhitePopVax)))
p1 + stat + stat2 + stat3
```
**Plot gamma probability density**
```{r}
gammaPars <- fitdistr(z$z.WhitePopVax,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="brown", n = length(z$z.WhitePopVax), args = list(shape=shapeML, rate=rateML))
 p1 + stat + stat2 + stat3 + stat4
```
**Plot beta probability density**
```{r}
pSpecial <- ggplot(data=z, aes(x=z.WhitePopVax/(max(z.WhitePopVax + 0.1)), y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
  xlim(c(0,1)) +
  geom_density(size=0.75,linetype="dotted")

betaPars <- fitdistr(x=z$z.WhitePopVax/max(z$z.WhitePopVax + 0.1),start=list(shape1=1,shape2=2),"beta")
shape1ML <- betaPars$estimate["shape1"]
shape2ML <- betaPars$estimate["shape2"]

statSpecial <- stat_function(aes(x = xval, y = ..y..), fun = dbeta, colour="orchid", n = length(z$z.WhitePopVax), args = list(shape1=shape1ML,shape2=shape2ML))
pSpecial + statSpecial
```

### Simulating New Data Set
```{r}
normPars <- fitdistr(z$z.WhitePopVax,"normal")
print(normPars) 

SimData <- rnorm(n=z$X1.46, mean = normPars$estimate["mean"], sd = normPars$estimate["sd"])

SimData <- data.frame(1:46, SimData)

p2 <- ggplot(data=SimData, aes(x=SimData, y=..density..)) +
    geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
 print(p2)
 

gammaPars <- fitdistr(SimData$SimData,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="brown", n = length(SimData$SimData), args = list(shape=shapeML, rate=rateML))
 p2 + stat
 
```

#### Graph of Original Data Set:
```{r}
p1 + stat4
```

#### Graph of Simulated Data Set:
The probability curves look very similar across the original data set and the simulated data set! 
```{r}
p2 + stat
```